%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                     Bachelor thesis template
%						 Science Faculty
%								at
%			National Autonomous University of Mexico (UNAM)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% based on Harish Bhanderi's PhD/MPhil template, then Uni Cambridge
% http://www-h.eng.cam.ac.uk/help/tpl/textprocessing/ThesisStyle/
% corrected and extended in 2007 by Jakob Suckale, then MPI-iCBG PhD programme
% and made available through OpenWetWare.org - the free biology wiki
%
%                     Under GNU License v3
%
% Adapted for the Engineering School at UNAM by Jesús Velázquez y Marco Ruiz
% Then, adapter fot he Science Faculty at UNAM by Jonathan Urrutia
%
%
%
% All used packages are found in
%
%					./Latex/Classes/PhDthesisPSnPDF.cls
%
% within this last document, there are some lines to be UnCommented for a printed or a digital version of the output file:
%
%			line 184
%			lines 231-261hfill
%
%	Since this is a template for a thesis made at UNAM (Mexico) the titles may be in spanish but within PhDthesisPSnPDF.cls it can be change
%

\documentclass[11pt]{Latex/Classes/PhDthesisPSnPDF}

\usepackage{blindtext}         %  For dummy text.
% The \blindtext or \Blindtext commands throughout this template generate dummy text to fill the template out.

\input{Latex/Comands}           % Special commands written by the author


\svgpath{{1-Theory/figs},{5-Apendices/figs},{2-Results/figs}}
\graphicspath{{5-Apendices/figs},{0-5-Introduccion/figs}}
\lstset{basicstyle=\ttfamily\footnotesize,breaklines=true}


\usepackage{Latex/mmacells}
\usepackage{Latex/coffee4}
\usepackage{rotating}

\mmaDefineMathReplacement[≤]{<=}{\leq}
\mmaDefineMathReplacement[≥]{>=}{\geq}
\mmaDefineMathReplacement[≠]{!=}{\neq}
\mmaDefineMathReplacement[→]{->}{\to}[2]
\mmaDefineMathReplacement[⧴]{:>}{:\hspace{-.2em}\to}[2]
\mmaDefineMathReplacement{∉}{\notin}
\mmaDefineMathReplacement{∞}{\infty}
\mmaDefineMathReplacement{𝕕}{\mathbbm{d}}


\mmaSet{
  morefv={gobble=2},
  linklocaluri=mma/symbol/definition:#1,
  morecellgraphics={yoffset=1.9ex}
}
\allowdisplaybreaks
\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}

%%-------------------------------------------------------------------------------
%                                  Information of the Student
%-------------------------------------------------------------------------------
% --- Default information for Bachelor's degree
%\author{Jonathan Alexis Urrutia Anguiano}
%\title{Optical response of partially embedded nanospheres}
%\programa{Posgrado en Ciencias Físicas} % Licenciatura en Física
%\degree{Maestro en Ciencias}% Maestro en / Doctor en
%\director{Dr. Alejandro Reyes Coronado}% Thesis director
%\facultad{Facultad de Ciencias}
%\lugar{Ciudad de México, México}% Place of the dissertation
%\degreedate{2021}% Year of the dissertation
%\portadatrue   %Uncomment for color cover

% ----------------------------- Datos del jurado de Licenciatura
%\student{Paternal last name\\ Maternal Last name\\ Names\\ Telephone number\\ Universidad Nacional Autónoma de México\\ Facultad de Ciencias\\ Física\\ Student Number}
%\secretario{Dr \\ Secretary (thesis director) \\ Last name \\ Last name}
%\presidente{Dr \\ President \\ Last name \\ Last name}
%\vocal{Dr \\ Vocal \\ Last name \\ Last name}
%\supuno{Dr \\ substitute 1 \\ Last name \\ Last name}
%\supdos{Dr \\ Substitute 2 \\ Last name \\ Last name}
%\pags{pages}


% --- Default information for Grad degree

\posgradotrue
	 \author{Jonathan Alexis Urrutia Anguiano}
		 \title{Optical response of partially embedded nanospheres}
		 \programa{Posgrado en Ciencias Físicas} 	% Programa de posgrado
		  \degree{Maestro en Ciencias}				% Maestro en / Doctor en

	\director{Dr. Alejandro Reyes Coronado}		% Thesis director
	\directordep{Facultad de Ciencias, UNAM}

	\lugar{Ciudad de México, México}			% Place of the dissertation
	\degreedate{2022} 							% Year of the dissertation  - Arreglar espacio inicial
	\campo{Física}								% Area del posgrado

	\comitetrue									% Comité académico en la portada
											% Falta ver si se ponen extra dentro del documento
		\ctutoruno{Dra. Citlali Sánchez-Aké}
		\ctutorunodep{Instituto de Ciencias Aplicadas y Tecnología, UNAM}
		\ctutordos{Dr. Giuseppe Pirruccio}
		\ctutordosdep{Instituto de Física, UNAM}

\keywords{tesis,autor,tutor,etc}            % For metadata
\subject{tema_1,tema_2}                     % Subjects for metadata














%-------------------------------------------------------------------------------
%                                   COVER
%-------------------------------------------------------------------------------
\begin{document}
%
\maketitle
%-------------------------------------------------------------------------------
%                                   FRONT MATTER
%-------------------------------------------------------------------------------
\frontmatter

\include{0-1-Acknowledgments/1-Acknowledgments}
%\include{0-2-Declaration/1-Declaration}
\include{0-3-Quote/1-Quote}
\include{0-4-Resumen/1-Resumen}

%-------------------------------------------------------------------------------
%                                INDICES                                    |
%-------------------------------------------------------------------------------
%
\setcounter{secnumdepth}{3} % organizational level that receives a numbers
\setcounter{tocdepth}{3}    % print table of contents for level 3
 
\tableofcontents            % Print main index


%-------------------------------------------------------------------------------
%                                MAIN MATTER
%-------------------------------------------------------------------------------
% the main text starts here with the introduction, 1st chapter,...
\mainmatter

\def\baselinestretch{1}                   % Line spacing

\input{0-5-Introduccion/1-Motivation-Structure}

%\part{Theoretical Framework}
\chapter{Scattering Theory of a Single Spherical Particle}
  \label{ch:OpticalProperties}

  The problem addressed in this thesis corresponds to the numerical analysis of the Localized Surface Plasmon Resonances (LSPR) \index{Plasmon!Localized Surface Plasmon Resonance (LSPR)} excited on plasmonic spherical nanoparticles (NPs) when these are under realistic experimental conditions, such as those found in plasmonic biosensors, where the NPs are partially embedded in a substrate \cite{moirangthem_enhanced_2012}. The performed analysis consists on the numerical calculation of the absorption, scattering and extinction  cross sections of a partially embedded metal NP, employing the Finite Element Method (FEM). To verify the validity of the obtained numerical results, the problem of the absorption and scattering of light by a single free-standing spherical particle is considered. In this chapter, we revisit the general solution of the light absorption and scattering by both an arbitrary particle and a spherical particle, given by the Mie Theory\footnote{The term \emph{Mie Theory} refers rather to a solution set to Maxwell's equations for the scattering of an electromagnetic plane wave due to a spherical particle, developed by Gustav Mie and published on 1907 \cite{mie_beitrage_1908}. Ludvig Lorenz published beforehand an equivalent solution to the same scattering problem nevertheless, Mie's solution consists in an iterative method suited for easier computations, which boosted its spread \cite{horvath_gustav_2009}. } \cite{bohren_absorption_1983}.

	\section{The Optical Theorem: Amplitude Matrix and Cross Sections}
	 \label{s:AmpMatCrossSect}
	 \input{1-Theory/1-OpticalTheorem}

	\section{Mie Scattering}
	  \label{s:Mie}

     In the previous Section, it was concluded that the extinction of light due to the interaction between a particle and a monochromatic plane wave can be determined through the amplitude of the scattered field in the forward direction. This is stated in the Optical Theorem, which is an exact relation, but inaccuracies may arise when either the scattering amplitude matrix or the extinction cross section are approximated\footnote{See for example Section 2.4 from Ref. \cite{tsang_scattering_2000} on the Rayleigh Scattering, and Section 21.7 from Ref. \cite{zangwill_modern_2013} on Thompson scattering.}. A particular case in which the scattering amplitude matrix can be exactly calculated is when the scatterer has spherical symmetry. In order to address this special case, it will be introduced a vectorial basis with spherical symmetry, known as the Vector Spherical Harmonics (VSH). Once the VSH are defined, they will be used to write a monochromatic plane wave in terms of the VSH. By imposing the continuity of the tangential components of the electric and magnetic fields, the scattered field can be also written in terms of the VSH. As a particular example of interest, shown in the last Section, the optical properties of a gold nanoparticle with radius of $12.5$ nm are calculated.

     % ------------------------------- index entries --------
     \index{Scattering!Thompson}%
     \index{Scattering!Mie}%
     \index{Scattering!Rayleigh}%
     \index{Vector!Spherical Harmonics}%

	    \subsection{Vector Spherical Harmonics}
		 \label{ss:VSH}
		 \input{1-Theory/2-VSH}

        \subsection{Incident, Scattered, and Internal Electric Fields}
	     \label{ss:Fields}
         \input{1-Theory/3-0-Fields}

        \subsection{Optical Properties of a Single Spherical (Gold) Particle}
		 \label{ss:AuMie}

         In previous Sections, the general theory for the light scattering was developed, introducing the scattering amplitude matrix $\mathbb{F}$ [Eq. \eqref{eq:ScatAmpMat}]. Then, the particular problem of a spherical scatterer was addressed and explicit expressions for the scattered electric field [Eq. \eqref{eq:EFar}] and for $\mathbb{F}$ were obtained [Eq. \eqref{eq:FscaS}] in terms of the Mie coefficients $a_\ell$ and  $b_\ell$ [Eqs. \eqref{eq:MieCoef}], as well as the internal electric field inside the scatterer [Eq. \eqref{eq:Eint}] in terms of the coefficients $c_\ell$ and $d_\ell$ [Eqs. \eqref{eq:coeffInt}]. The  optical properties of a particle is related to the electric field outside the scatterer,  and can be studied within two different spatial regions: the near-field and the far-field regimes. The near-field region consists in the complete analytical solution of the scattered electric field [Eq. \eqref{eq:EscaLC}], while the far-field regime considers only the contributions proportional to $r^{-1}$, with $r$ the distance between the center of the scatterer and the measurement point; the optical properties in the far-field regime can be determined by the scattering amplitude matrix $\mathbb{F}$ itself.  In this last Section, the previous results are employed to calculate the optical properties of  a spherical gold nanoparticle (AuNP) with a radius of $12.5$ nm, either embedded in an of air or in a glass matrix, when it is illuminated by an incident plane wave with a wavelength $\lambda$.

            \subsubsection{Localized Surface Plasmons}
             \label{sss:LSPR}
             \input{1-Theory/3-1-AuMieLSPR}

            \subsubsection{Far-Field Optical Properties}
             \label{sss:FarField}
             \input{1-Theory/3-2-AuMieFar}


\chapter{The Finite Element Method}
 \label{chapter:FEM}

    Several physical problems are described by systems of partial differential equations (PDE) alongside boundary or initial conditions, whose analytical solution can be achieved only in some cases. For example, the scattering of light due to an arbitrary spherical particle, described by the vectorial Helmholtz equation [Eq. \eqref{eq:Helmholtz}] with the boundary conditions at the surface of the spherical particle given by Eq. \eqref{eq:contuinity},   is one of the few physical problems with an analytical solution. Nevertheless, it is set in an ideal scenario where the particle is a perfect sphere, it is isolated and embedded in a non-absorbing matrix. Any of  these conditions on the geometry and physical properties of the described system were to change, the scattering problem may not have an analytical solution;  for such cases one alternative is to employ a numerical approach to find an approximated solution.  Among the numerical methods employed in Electrodynamics, one of them is the Finite Element Method (FEM).

    In this Chapter the theory behind the FEM is presented with its implementation on the light scattering problem. In Section \ref{s:FEM-Fund} fundamentals of the FEM are explained: the Galerkin method and the concept of the finite element. In Section \ref{s:Scat-FEM}, the light scattering problem is revisited so it can be approached through an integral formulation, allowing the use of the FEM since a generalization of the concepts seen in Section \ref{s:FEM-Fund}  into vectorial quantities is needed, as well as the introduction of boundary conditions in open regions so an infinite medium problem, such as the light scattering, can be approached numerically. In the last section, the scattering problem of an isolated spherical particle, addressed in Chapter \ref{ch:OpticalProperties}, is solved analytically and numerically ---employing the commercial software COMSOL Multiphysics\texttrademark{} Ver. 5.4--- and their results are contrasted.

    \section{Fundamentals}
     \label{s:FEM-Fund}
     \input{1-Theory/4-1-Fundamentals}

        \subsection{The Finite Element Approximation}
         \label{ss:FEM-FE}
         \input{1-Theory/4-2-FE}

    \section{Numerical Approach to the Light Scattering Problem}
     \label{s:Scat-FEM}

    In Chapter \ref{ch:OpticalProperties} the general theory of isolated scatterers in a non-absorbing media was developed and the particular case of spherical scatterers was approached analytically. In order to solve the light scattering problem through numerical methods and thus allowing for more complex geometries, the fundamentals of the Finite Element Method (FEM) were introduced in Section \ref{s:FEM-Fund}. Hereby, it is discussed the implementation of the FEM into the light scattering problem to find numerical approximations, in the weak sense, to the  electric field $\vb{E}(\vb{r})$ in finite domain $\Omega$. Due to the vectorial nature of the electric field, the interpolating ---and trial--- functions employed in the Galerkin method [Eq. \eqref{eq:GalerkinMat}] are chosen to be vectorial functions instead of scalar functions, since a family of vectorial finite element can be chosen so the boundary conditions of the electric fields are easily met. In this Section, the strong and weak formulations of the scattering of light are developed by employing such vectorial interpolating functions, and the corresponding finite elements are introduced, as well as the matrix representation of the light scattering problem. Lastly, additional conditions are imposed into the light scattering problem in order to solve it numerically through the FEM.

        \subsection{Strong and Weak Formulations}
         \label{ss:Scat-Form}
         \input{1-Theory/5-Strong-Weak}

         \subsection{The Nédélec Finite Element Family}
          \label{ss:Nedelec}
         \input{1-Theory/6-0-Vectorial-FEM}

        \subsection{Open Boundary Conditions }
         \label{ss:Sommerfeld-PML}

        In the previous Sections the theory behind the FEM and how it is  implemented into the light scattering problem [Eqs. \eqref{eq:Scatt-Weak-All}] was discussed. A special kind of boundary conditions, known as the Absorbing Boundary Conditions (ABC), are introduced in this Section since numerical methods, such as the FEM, require the domain $\Omega$, where the electromagnetic fields are to be solved, to be of finite size \cite{jin_theory_2010,bondeson_computational_2005} while in the scattering problem an infinite ---or open--- boundary is considered. The  ABCs are required since they simulate an open domain with a finite domain $\Omega$ by imposing that there are no reflections back into the domain due to the interaction between its boundary $\partial\Omega$ and the scattered electric field \cite{bondeson_computational_2005,jin_theory_2010,chew_complex_1997}. Two of the most common ABCs are the Sommerfeld's radiation condition ---which describes the behavior of the electric field in the far-field at $\partial\Omega$--- and the Perfectly Matching Layer (PML) ---which is a thin layer that covers $\Omega$ and acts as a non-reflective material---\cite{jin_theory_2010}.  Both of the previous ABCs are preferred over other kinds of ABC since they do not need the domain $\Omega$ to grow considerably and thus are optimized for the FEM while its implementation faces no extra difficulties \cite{jin_theory_2010}.
        \index{Boundary Conditions!Open}%
        \index{Boundary Conditions!Absorbing}%
        \index{Partial Differential Equation (PDE)!Boundary Conditions!Open}%
        \index{Partial Differential Equation (PDE)!Boundary Conditions!Absorbing}%

         \input{1-Theory/7-0-OpenBoundary}

	\section{Finite Element Method and Analytical Solutions}
		\label{sec:FEM-Mie}
		\input{1-Theory/4-FEM}

%

\chapter{Results and Discussion}
	\label{ch:Results}

    The problem of the absorption and scattering of light by a single nanoparticle (NP), illuminated by a monochromatic plane wave, is analytically described by the Mie Theory (Section \ref{s:Mie}) if the NP is considered to be embedded in an infinite medium (the matrix). When more realistic conditions are considered, such as the presence of a second medium (the substrate) forming a planar interface with the matrix and the possibility of a partial embedding of the NP inside the substrate, the Mie Theory is no longer adequate to study the optical properties of such systems. In this Chapter, the optical response of a gold (Au) spherical NP of radius $a = 12.5$ nm, below, above, and at a planar interface between air and glass is calculated through the Finite Element Method (FEM), when a monochromatic plane wave of wavelength $\lambda$ traveling in the direction $\vb{k}^\text{i}$ illuminates the system at an angle of incidence $\theta_i$, considering a defined polarization state of the incident electric field $\vb{E}^\text{i}$. To identify the effect of the substrate and the embedding of the NPs inside the substrate, the absorption and scattering  efficiencies [Eqs. \eqref{eq:Csca}, \eqref{eq:Cabs} and \eqref{eq:Efficiencies}], as well as the radiation pattern (see Fig. \ref{fig:ScatteringMaps}) and the distribution of the induced electric field on and inside the NP (see Fig. {fig:NearField}) are calculated numerically for the desired geometries and compared with limiting cases of the Mie theory: a AuNP isolated in a matrix of air and in a matrix of glass.

    The aforementioned analysis is organized as follows: In Section \ref{s:Totally} it is addressed the extreme cases of the supported and the totally embedded NP illuminated at normal incidence (Section \ref{s:Totally:Normal}) and at oblique incidence (Section \ref{s:TIR}), while in Section \ref{s:Emb} the effect of the partially embedding is studied considering once again  normal (Section \ref{s:Emb:Normal}) and oblique (Section \ref{s:Emb:Obl}) incidence.

    \section{Supported and Totally Embedded Spherical Particles}
     \label{s:Totally}
        \input{2-Results/0-Intro}

        \subsection{Normal Incidence}
        \input{2-Results/1-Totally}
         \label{s:Totally:Normal}
         
         \subsection{Supported Spherical Particle in Total Internal Reflection}
         \label{s:TIR}
         \input{2-Results/2-Supported}

    \section{Partially Embedded Spherical Particle}
    \label{s:Emb}
       \input{2-Results/3-Part-Intro}

       \subsection{Normal Incidence}
       \input{2-Results/4-Embedded-Normal}
         \label{s:Emb:Normal}

        \subsection{Partially Embedded Spherical Particle in Total Internal Reflection}
        \input{2-Results/5-Embedded-Oblique}
         \label{s:Emb:Obl}

\chapter*{Conclusions}
\addcontentsline{toc}{chapter}{\protect\numberline{}Conclusions}
	\label{ch:Conclusions}
	\input{3-Conclusions/1-Conclusions}	
	
    \section*{Future Work: Application on Metasurfaces}
    \addcontentsline{toc}{section}{\protect\numberline{}Future Work: Application on Metasurfaces}
    \label{s:FWork}
    \input{3-Conclusions/2-Future}	

\appendix

\chapter{Mie Theory (Conventions)}
  \label{app:MieCode}
  \input{5-Apendices/1-SpecialFunc}

\chapter{Size Correction to the Dielectric Function}
    \label{app:SizeCorrection}
    \input{5-Apendices/2-SizeCorrection}

\chapter{Brief COMSOL Implementation of the Scattering Problem}
    \label{app:COMSOL}
    \input{5-Apendices/3-COMSOL_Implementation}


%%-------------------------------------------------------------------------------
%%                               References                                   |
%%-------------------------------------------------------------------------------
%
%\appendix
%\input{5-Apendices/1-Something_extra.tex}

\setlength\bibitemsep{.1\itemsep}
\printbibliography

\newpage
%: ----------------------- list of figures/tables ------------------------
%\listoffigures              % Genera el ínidce de figuras, comentar línea si no se usa
%\listoftables               % Genera índice de tablas, comentar línea si no se usa
\printindex
%-------------------------------------------------------------------------------
%                              Appendix                                   |
%-------------------------------------------------------------------------------



\end{document}
